Scalar on Function Regression \\ with Applications to Near-Infrared Spectroscopy

### 2022-01-14 Presentation/slides.tex
Correction
Increment

% Title page details: 
\title{Scalar on Function Regression \\
with Applications to Near-Infrared Spectography}
\author{Jonathan Willnow, Jakob Juergens, Jonghun Baek}
\date{{\color{red}}Presentation Day}

@@

		$$\beta(t) = \sum_{j = 1}^{\infty} c_j \phi_j(t) \approx \sum_{j = 1}^{L} c_j b_j(t)$$
		%Assume that we have a data set containing observations each of which is made up of:
		%\begin{itemize}
		%	\item $y_i$: a scalar realization of $Y(\omega)$ - the octane rating of gasoline
		%	\item $x_i(t)$: a realization of $X(\omega)$ - the measured NIR spectrum
		%\end{itemize}

@@

	\begin{frame}{Estimation via Basis Representation}
		Each combination of $x_i(t)$ and $\phi_j(t)$ gives us
		$$Z_{i,j} = \int_{0}^{1} x_i(s) b_j(s)\mathrm{d}s$$

@@

		\textbf{Empirical Mean Function}:
		$$\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}f_j(t)$$

		\textbf{Empirical Autocovariance Function}:
		$$\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(f_j(t) - \hat{\mu}(t)\right) \left(f_j(s) - \hat{\mu}(s)\right)$$

@@

	\begin{frame}{FPCA - Plots}
			%\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}
			\includegraphics[width = \textwidth]{../Graphics/pc_approx.pdf}
	\end{frame}

>>>>

% Title page details: 
\title{Scalar on Function Regression \\
with Applications to Near-Infrared Spectroscopy}
\author{Jonathan Willnow, Jakob Juergens, Jonghun Baek}
\date{18.01.2022}

@@

		$$\beta(t) = \sum_{j = 1}^{\infty} c_j \phi_j(t) \approx \sum_{j = 1}^{L} c_j \phi_j(t)$$
		%Assume that we have a data set containing observations each of which is made up of:
		%\begin{itemize}
		%	\item $y_i$: a scalar realization of $Y(\omega)$ - the octane rating of gasoline
		%	\item $x_i(t)$: a realization of $X(\omega)$ - the measured NIR spectrum
		%\end{itemize}

@@

	\begin{frame}{Estimation via Basis Representation}
		Each combination of $x_i(t)$ and $\phi_j(t)$ gives us
		$$Z_{i,j} = \int_{0}^{1} x_i(s) \phi_j(s)\mathrm{d}s$$

@@

		\textbf{Empirical Mean Function}:
		$$\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}x_j(t)$$

		\textbf{Empirical Autocovariance Function}:
		$$\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(x_j(t) - \hat{\mu}(t)\right) \left(x_j(s) - \hat{\mu}(s)\right)$$

@@

	\begin{frame}{FPCA - Plot}
			%\includegraphics[width = \textwidth]{../Graphics/principal_components.pdf}
			\includegraphics[width = \textwidth]{../Graphics/pc_approx.pdf}
	\end{frame}
